Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more parspec section

A general procedure to describe deviations from the Kerr QNM frequencies $\omega_{J}^{\rm K}$ and
damping times $\tau_{J}^{\rm K}$ is to write,
%
\begin{subequations}
\label{eq:general_deviation}
\begin{align}
\omega_{J} &= \omega^{\rm K}_{J} \, (1 + \delta \omega_{J}), \\
\tau_{J}   &= \tau^{\rm K}_{J}   \, (1 + \delta \tau_{J}),
\end{align}
\end{subequations}
%
where $\delta\omega_{J}$ and $\delta\tau_{J}$ are the deformation parameters.
%
Here we use the subscript $J$ to represent the QNM labels $\{l,\, m,\, n\}$,
where $l$ and $m$ are the multipole indices, and $n$ the overtone number.
%
We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
QNM in this work, that is, $J = \{2,\, 2,\, 0\}$.
%
This approach was adopted, e.g., in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.

@@

@@

Let us now establish the connection between theory-agnostic framework of the
$\pSEOB$ waveform model and the theory-specific QNM calculations.
%
We begin by expanding $\omega$ and $\tau$, given by Eqs.~\eqref{eq:kerr_expansion} as,
%
\begin{subequations}
\label{eq:qnm_nongr_iso}
\begin{align}
M \omega_{220} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
+ \sum_{n=0}^{N_{\rm max}} \chi^{j} \omega^{j}\,,
\\
\tau_{220}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
+ \sum_{n=0}^{N_{\rm max}} \chi^{j} \tau^{j}\,,
\end{align}
\end{subequations}
%
where, recall, we focus on the $\ell = m = 2$, $n=0$ QNM and have pulled out of
the sum all beyond-GR corrections, restricting ourselves to the nonspinning
($n=0$) and linear-order in spin ($n=1$) corrections to the Kerr QNMs.
%
These corrections are encoded in the coefficients $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$.

>>>>

A general procedure to describe deviations from the Kerr QNM frequencies $\omega_{J}^{\rm K}$ and
damping times $\tau_{J}^{\rm K}$ is to write,
%
\begin{subequations}
\label{eq:general_deviation}
\begin{align}
\omega_{J} &= \omega^{\rm K}_{J} \, (1 + \delta \omega_{J}), \\
\tau_{J}   &= \tau^{\rm K}_{J}   \, (1 + \delta \tau_{J}),
\end{align}
\end{subequations}
%
where $\delta\omega_{J}$ and $\delta\tau_{J}$ are the deformation parameters.
%
Here we use the subscript $J$ to represent the QNM labels $\{l,\, m,\, n\}$,
where $l$ and $m$ are the multipole indices, and $n$ the overtone number.
%
This approach was adopted, e.g., in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.

@@

We remark that in the GR limit, where $\delta\omega_{J}^{(n)} = \delta\tau_{J}^{(n)} = 0$ $\forall\, n$,
the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
the Kerr QNMs for spins $\chi \lesssim 0.7$.
%
The values of the fitting coefficients $\omega_{J}^{(n)}$ and $\tau_{J}^{(n)}$
can be found in Ref.~\cite{Maselli:2019mjd}, Table I.

@@

Let us now establish the connection between theory-agnostic framework of the
$\pSEOB$ waveform model and the theory-specific QNM calculations.
%
We begin by expanding $\omega$ and $\tau$, given by Eqs.~\eqref{eq:kerr_expansion} as,
%
\begin{subequations}
\label{eq:qnm_nongr_iso}
\begin{align}
M \omega_{220} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
+ \sum_{n=0}^{N_{\rm max}} \chi^{j} \omega^{j}\,,
\\
\tau_{220}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
+ \sum_{n=0}^{N_{\rm max}} \chi^{j} \tau^{j}\,,
\end{align}
\end{subequations}
%
We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
QNM in this work, that is, $J = \{2,\, 2,\, 0\}$, and we  have pulled out of
the sum all beyond-GR corrections, restricting ourselves to the nonspinning
($n=0$) and linear-order in spin ($n=1$) corrections to the Kerr QNMs.
%
These corrections are encoded in the coefficients $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$.
